How predictable is extinction?

### 2019-04-03 doc/norcalpaleo2019_talk.tex
norcalpaleo talk if needed

        \attrib{\footnotesize{UCL}}
      \end{center}
    \end{column}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/occ_time_label}
    \end{column}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/age_label}
    \end{column}
  \end{columns}

@@

    \end{column}
    \begin{column}{0.6\textwidth}
      \[
        \text{AUC} = 
        \begin{cases} 
          0.5 & \text{non discrimination}\\
          0.6-0.7 & \text{poor} \\
          0.7-0.8 & \text{acceptable/fair} \\
          0.8-0.9 & \text{excellent/good} \\
          > 0.9 & \text{outstanding} \\
        \end{cases}
      \]

      The area represents the probability of correct ranking of a random ``extinct''-``extant'' pair.
    \end{column}
  \end{columns}

@@

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/auc_hist}

@@

\begin{frame}
  \frametitle{In-sample predictive performance, by time}

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/auc_ts}
  \end{center}

@@

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/fold_auc_zoom}

@@

\begin{frame}
  \frametitle{Cross-validation results, by time}

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/fold_auc_time}
  \end{center}

>>>>

        \attrib{\footnotesize{UCL}}
      \end{center}
    \end{column}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/occ_time_label_full}
    \end{column}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/age_label_full}
    \end{column}
  \end{columns}

@@

    \end{column}
    \begin{column}{0.6\textwidth}
      The area represents the probability of correct ranking of a random ``extant''-``extinct'' pair.

      \[
        \text{AUC} = 
        \begin{cases} 
          0.5 & \text{non discrimination}\\
          0.6-0.7 & \text{poor} \\
          0.7-0.8 & \text{acceptable/fair} \\
          0.8-0.9 & \text{excellent/good} \\
          > 0.9 & \text{outstanding} \\
        \end{cases}
      \]

    \end{column}
  \end{columns}

@@

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/auc_hist_full}

@@

\begin{frame}
  \frametitle{In-sample predictive performance, by time and taxa}

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/auc_taxon_time_full}
  \end{center}

@@

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/fold_auc_zoom_full}

@@

\begin{frame}
  \frametitle{Cross-validation results, by time and taxa}

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/fold_auc_taxon_time_full}
  \end{center}
